\mytitle

### 2016-06-06 report/paper.tex
Rewrite a part of the contributions subsection

\subsection{Contribution}
Until now, the creators of EpTO have only tested this algorithm in a simulated environment. In this work, we implement EpTO in pure Kotlin using the NeEM library \autocite{neem} and show that EpTO is actually suitable for real-world large-scale distributed systems. We then evaluate EpTO by comparing it to the deterministic total order algorithm provided by JGroups  \autocite{jgroups} in both stable (no-churn) and unstable systems. These comparisons help us verify if EpTO is actually performing as expected in a real-world scenario.
\todo[inline]{Here we will present our conclusion briefly}
\par
These tasks are split in two parts. The first part will assume that all peers are known by all peers. We will implement EpTO using this assumption and test it against JGroups. In the second part of the tasks, we will assume unknown membership on all peers, meaning, peers never have a full view  of all the peers. We will update EpTO and use a PSS\footnote{Peer Sampling Service} to find peers to exchange with. We will then update the underlying layer NeEM to use UDP instead of TCP and switch to NIO.2 \autocite{nio}.

@@

\subsection{Ordering Component}
The Ordering component is responsible for ordering events before delivering them to the application.
To achieve this, the Ordering component has a \textit{received} hash table of (\textit{id}, \textit{event}) pairs containing all the events which are received by the peer, but not yet delivered to the application and a \textit{delivered} hash table containing all the events which were delivered.
\par
In brief, the Ordering component first increments the timestamp of all the events which have been received in previous rounds to indicate the start of a new round. Then, it processes new events in the received ball by discarding events that have been received already (delivered events or events with timestamp smaller than the last delivered event). This is done to prevent delivering duplicate events. The remaining events in the received ball will be added to the \textit{received} hash table, and wait to be delivered based on the Stability oracle.
\subsection{Stability Oracle}
The Stability oracle is the component that outputs timestamps. It will increment its local clock every round as well as synchronize itself using timestamps of newly received events, to make sure the local clock does not drift too much.
\par
This Stability oracle offers an API to the Ordering component letting it know when an event is mature enough to be delivered to the application.
\par
As this component is local and only corrects itself when we receive new events, it generates no network traffic. This means it does not impact the scalability of EpTO.
\section{Performance Comparisons}
In the following subsections, we will present the results obtained for the different tests ran and explain their meanings.
\subsection{Methodology}
Our tests are run on a cluster provided by the University of Neuchâtel. We use OpenNebula \autocite{opennebula} to manage our cluster of virtual machines. We make use of Docker \autocite{docker}. More specifically we use Docker-compose, which is a tool to run multi-container applications, coupled to docker-swarm, which lets us make a pool of Docker hosts appear as a single Docker host.
\par
Each peer is hosted in a Docker container. We want to test JGroups and EpTO and find at which point JGroups breaks latency and throughput wise. At this point EpTO should still be working. Under this treshold, JGroups should be faster than EpTO but EpTO should still hold its own.
\subsection{Peer membership known}
\todo[inline]{We will present the results obtained and try to explain the results}

>>>>

\subsection{Contribution}
Until now, the creators of EpTO have only tested this algorithm in a simulated environment. In this work, we implement EpTO in pure Kotlin using a modified version of the NeEM library \autocite{neem} and show that EpTO is actually suitable for real-world large-scale distributed systems. The modification to NeEM includes a dumbed-down gossip dissemination as seen in \autocite{matos2015epto}. We then evaluate EpTO by comparing it to the deterministic total order algorithm provided by JGroups  \autocite{jgroups} in both stable (no-churn) and unstable systems. These comparisons help us verify if EpTO is actually performing as expected in a real-world scenario.
\todo[inline]{Here we will present our conclusion briefly}
\par
In our experiments we assume each peer knows every other peers. We implement EpTO using this assumption and test it against JGroups. The details concerning the methodology are explained in subsection \ref{sub:metho}. In future works, we want to test EpTO when not knowing the entire membership.

@@

\subsection{Ordering Component}
The Ordering component is responsible for ordering events before delivering them to the application.
To achieve this, the Ordering component has a \textit{received} hash table of (\textit{id}, \textit{event}) pairs containing all the events which are received by the peer, but not yet delivered to the application and a \textit{delivered} hash table containing all the events which were delivered.
\par
In brief, the Ordering component first increments the timestamp of all the events which have been received in previous rounds to indicate the start of a new round. Then, it processes new events in the received ball by discarding events that have been received already (delivered events or events with timestamp smaller than the last delivered event). This is done to prevent delivering duplicate events. The remaining events in the received ball will be added to the \textit{received} hash table, and wait to be delivered based on the Stability oracle.
\subsection{Stability Oracle}
The Stability oracle is the component that outputs timestamps. It will increment its local clock every round as well as synchronize itself using timestamps of newly received events, to make sure the local clock does not drift too much.
\par
This Stability oracle offers an API to the Ordering component letting it know when an event is mature enough to be delivered to the application.
\par
As this component is local and only corrects itself when we receive new events, it generates no network traffic. This means it does not impact the scalability of EpTO.
\section{Performance Comparisons}
In the following subsections, we will present the results obtained for the different tests ran and explain their meanings.
\subsection{Methodology}
\label{sub:metho}
Our tests are run on a cluster provided by the University of Neuchâtel. We use OpenNebula \autocite{opennebula} to manage our cluster of virtual machines. We make use of Docker \autocite{docker}. More specifically we use Docker-compose, which is a tool to run multi-container applications, coupled to docker-swarm, which lets us make a pool of Docker hosts appear as a single Docker host.
\par
Each peer is hosted in a Docker container. We want to test JGroups and EpTO and find at which point JGroups breaks latency and throughput wise. At this point EpTO should still be working. Under this treshold, JGroups should be faster than EpTO but EpTO should still hold its own.
\subsection{Peer membership known}
\todo[inline]{We will present the results obtained and try to explain the results}
